### 2021-03-02 Presentazione/Presentation.tex
PUB

\begin{frame}
\frametitle{Abbigliamento}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Abbigliamento_RAW.pdf}\\
\includegraphics[width=5cm,height=4cm]{Pic/Abbigliamento.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Abbigliamento_Matrix.pdf}\\
\begin{itemize}
\item Rosso: Alimentari
\end{itemize}
\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.33  & 0.07  \\ \hline
$\delta_{T1}$   & -40.16 & 2.30  \\ \hline
$\delta_{T2}$   & -60.07 & 3.1   \\ \hline
$\delta_{T3}$   & -16.45 & 3.17 
\end{tabular}
\end{table}

@@

\begin{frame}
\frametitle{Calzature}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Calzature_RAW.pdf}\\
\includegraphics[width=5cm,height=4cm]{Pic/Calzature.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Calzature_Matrix.pdf}\\
\begin{itemize}
\item Rosso: Alimentari
\end{itemize}
\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.18  & 0.08  \\ \hline
$\delta_{T1}$   & -38.70 & 1.86   \\ \hline
$\delta_{T2}$   & -65.78 & 2.57  \\ \hline
$\delta_{T3}$   & -20.62 & 2.57 
\end{tabular}
\end{table}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{Elettrodomestici}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Elettrodomestici_RAW.pdf}\\
\includegraphics[width=5cm,height=4cm]{Pic/Elettrodomestici.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Elettrodomestici_Matrix.pdf}\\
\begin{itemize}
\item Rosso: Alimentari
\end{itemize}
\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.12  & 0.06  \\ \hline
$\delta_{T1}$   & -20.32 & 2.62   \\ \hline
$\delta_{T2}$   & -27.34 & 3.62  \\ \hline
$\delta_{T3}$   & -3.68 & 3.62
\end{tabular}
\end{table}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{Fotoottica}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Fotoottica_RAW.pdf}\\
\includegraphics[width=5cm,height=4cm]{Pic/Fotoottica.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Fotoottica_Matrix.pdf}\\
\begin{itemize}
\item Rosso: Alimentari
\end{itemize}
\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.40  & 0.07  \\ \hline
$\delta_{T1}$   & -34.14 & 2.76   \\ \hline
$\delta_{T2}$   & -52.32 & 3.82  \\ \hline
$\delta_{T3}$   & -7.86 & 3.82
\end{tabular}
\end{table}
\end{columns}
\end{frame}

>>>>

\begin{frame}
\frametitle{Abbigliamento}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Abbigliamento_RAW.pdf}\\
\includegraphics[width=5cm,height=3.5cm]{Pic/Abbigliamento.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Abbigliamento_Matrix.pdf}\\
\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.33  & 0.09  \\ \hline
$\delta_{T1}$   & -36.33 & 2.15  \\ \hline
$\delta_{T2}$   & -56.23 & 2.77   \\ \hline
$\delta_{T3}$   & -11.95 & 2.86 \\ \hline
$\delta_{T4}$ (Plc T= -3)   & 14.55  & 13.14 \\ \hline
$\delta_{T6}$ (Plc T= -1) & 13.90 & 13.30
\end{tabular}
\end{table}

@@

\begin{frame}
\frametitle{Calzature}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Calzature_RAW.pdf}\\
\includegraphics[width=5cm,height=4cm]{Pic/Calzature.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Calzature_Matrix.pdf}\\
\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.22  & 0.08  \\ \hline
$\delta_{T1}$   & -38.70 & 1.91   \\ \hline
$\delta_{T2}$   & -63.21 & 2.47  \\ \hline
$\delta_{T3}$   & -17.61 & 2.54  \\ \hline
$\delta_{T4}$ (Plc T= -3)   & 15.10  & 13.95 \\ \hline
$\delta_{T6}$ (Plc T= -1) & 15.36 & 14.12
\end{tabular}
\end{table}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{Elettrodomestici}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Elettrodomestici_RAW.pdf}\\
\includegraphics[width=5cm,height=4cm]{Pic/Elettrodomestici.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Elettrodomestici_Matrix.pdf}\\
\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.12  & 0.14  \\ \hline
$\delta_{T1}$   & -19.21 & 3.10   \\ \hline
$\delta_{T2}$   & -26.23 & 4.00  \\ \hline
$\delta_{T3}$   & -2.37 & 4.12  \\ \hline
$\delta_{T4}$ (Plc T= -3)   & 8.80  & 7.57 \\ \hline
$\delta_{T6}$ (Plc T= -1) & 4.86 & 7.66
\end{tabular}
\end{table}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{Fotoottica}
\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Fotoottica_RAW.pdf}\\
\includegraphics[width=5cm,height=4cm]{Pic/Fotoottica.pdf}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{Pic/Fotoottica_Matrix.pdf}\\

\begin{table}[]
\begin{tabular}{l|l|l}
                & Value  & Error \\ \hline
$\delta$ Slope before T1 & -0.36  & 0.12 \\ \hline
$\delta_{T1}$   & -29.94 & 2.73   \\ \hline
$\delta_{T2}$   & -48.11 & 3.52  \\ \hline
$\delta_{T3}$   & -2.93 & 3.63 \\ \hline
$\delta_{T4}$ (Plc T= -3)   & 8.87  & 78.87 \\ \hline
$\delta_{T6}$ (Plc T= -1) & 11.65 & 12.12
\end{tabular}
\end{table}
\end{columns}
\end{frame}
